Estimating SARS-CoV-2 transmission in England from randomly sampled prevalence surveys

### 2024-01-16 transmission.tex
Edit SEIR

The 11--16 age group (roughly corresponding to compulsory secondary school education) is estimated to have the highest incidence (see \cref{SEIR:fig:incidence}).
Incidence is smooth within each week but shows discontinuities between weeks.
This is because the parameters within $\matr{\beta}(t)$ are constant within each week.
A constant $\matr{\beta}(t)$ leads to exponential growth over short time periods, once the initial dynamics have died out.
When the peak in incidence is estimated to occur varied by region, but due to this reason, is almost always on a Sunday (see \cref{SEIR:fig:peak-incidence}).
For Yorkshire, the peak is estimated to occur in late October.
For all other regions, it is estimated to occur in late December or Early January, the period during which severe social distancing measures were applied.
\begin{figure}
    \includegraphics{SEIR/CIS/incidence}
    \caption[Posterior estimates of incidence]{%
        Posterior estimates (95\% CrI) of incidence by region and age.
        See main text for discussion.
    }
    \label{SEIR:fig:incidence}
\end{figure}
\begin{figure}
    \includegraphics{SEIR/CIS/p_peak}
    \caption[Posterior estimates of peak incidence timing]{%
        Posterior probability of the peak incidence for each region and age combination occurring on each day.
    }
    \label{SEIR:fig:peak-incidence}
\end{figure}

The parameters $\beta_w$ absorb all the time-varying changes in transmission not captured by Google mobility and school attendance data.
They trend downwards up until early December when they start increasing again.
Each region is estimated independently, however correlation is clear across the regions.

@@

The \emph{attack rate} is the proportion of the population that have been infected at least once\todo{cite attack rate}.
In this model it is $1 - \vec{s}$.
The attack rate is highest in the $[11, 16)$ age group in the North West at 50\% (95\% CrI: 48\%--52\%) (see \cref{SEIR:fig:attack-rates}).
\begin{figure}
    \includegraphics{SEIR/CIS/attack_rates}
    \caption{Posterior median and 95\% CrI of the attack rate in each region and age group.}
    \label{SEIR:fig:attack-rates}
\end{figure}

@@

\todo[inline]{discuss comparisons with the backcalculation, based on notes below (using preliminary results)}

>>>>

The 11--16 age group (roughly corresponding to compulsory secondary school education) is estimated to have the highest incidence (see \cref{SEIR:fig:incidence}).
Incidence is smooth within each week but shows discontinuities between weeks.
This is because the parameters within $\matr{\beta}(t)$ are constant within each week.
A constant $\matr{\beta}(t)$ would lead to exponential growth following a period of transitory dynamics, although the weekly switching may mean that these transitory dynamics never end, especially when incidence is high~\autocite{rhodesConvergence}.
When the peak in incidence is estimated to occur varied by region, but due to the switching, is almost always on a Sunday (see \cref{SEIR:fig:peak-incidence}).
For Yorkshire, the peak is estimated to occur in late October.
For all other regions, it is estimated to occur in late December or Early January, the period during which severe social distancing measures were applied.
\begin{figure}
    \includegraphics{SEIR/CIS/incidence}
    \caption[Posterior estimates of incidence]{%
        Posterior estimates (95\% CrI) of incidence by region and age.
        See main text for discussion.
    }
    \label{SEIR:fig:incidence}
\end{figure}
\begin{figure}
    \includegraphics{SEIR/CIS/p_peak}
    \caption[Posterior estimates of peak incidence timing]{%
        Posterior probability of the peak incidence for each region and age combination occurring on each day.
    }
    \label{SEIR:fig:peak-incidence}
\end{figure}

The $\beta_w$ parameters absorb all the time-varying changes in transmission not captured by Google mobility and school attendance data.
They trend downwards up until early December, then they start increasing (see \cref{SEIR:fig:beta-walk}).
Correlation is clear across the regions even though each region is estimated independently, suggesting underlying biological or epidemiological changes across regions as opposed to modelling assumptions.

@@

The \emph{attack rate} is the proportion of the population that have been infected at least once\todo{cite attack rate}.
In this model it is $1 - \vec{s}$.
The attack rate is highest in the $[11, 16)$ age group in the North West at 50\% (95\% CrI: 48\%--52\%) (see \cref{SEIR:fig:attack-rates}).
\begin{figure}
    \includegraphics{SEIR/CIS/attack_rates}
    \caption{Posterior median and 95\% CrI of the attack rate in each region and age group.}
    \todo[inline]{Maybe compare this to blood donors, as used in the prior.}
    \label{SEIR:fig:attack-rates}
\end{figure}

@@
